Rectangulotopes

### 2024-04-26 draft/rectangulotopes.tex
minor change

From the results of \cref{subsec:quotientopes}, the submodular function corresponding to our realization of $\SRP(n)$ can be obtained as before by summing the functions defining the yin and yang shard polytopes in \cref{lem:yinsp,lem:yangsp}.
Note again that all rays of the braid fan are preserved in the fan of the strong rectangulotope, hence our characterization of the strong rectangulotope is an irredundant facet description.

>>>>

From the results of \cref{subsec:quotientopes}, the submodular function corresponding to our realization of $\SRP(n)$ can be obtained as before by summing the functions defining the yin and yang shard polytopes in \cref{lem:yinsp,lem:yangsp}.
Note again that all rays of the braid fan are preserved in the fan of the strong rectangulotope, hence our submodular description of the strong rectangulotope is an irredundant facet description.
